Learning constraints in tabular data

### 2016-05-11 Paper/ECAI/tabular.tex
added a stab for the extension
Expanded error detection, small fixes conclusion

\newcommand{\constraints}{\ensuremath{\mathcal{T}}\xspace}
\newcommand{\format}[1]{\textit{#1}\xspace}
\newcommand{\generategroups}{\format{generateGroups}}
\newcommand{\extractgroups}{\format{extractGroups}}
\newcommand{\extracttables}{\format{extractTables}}
\newcommand{\learnconstraints}{\format{learnConstraints}}
\newcommand{\findassignment}{\format{findConstraints}}
\newcommand{\postprocess}{\format{pruneRedundant}}
\newcommand{\constrainttorder}{\format{templateOrder}}
\newcommand{\template}{\format{constraint template}}
\newcommand{\sname}{\format{TaCKLe}}

@@

% {\it
% \textbf{Motivation}:
% \begin{itemize}
%   \item USED -- File generated from model, model got lost, need to reconstruct
%   \item Constraint programming is hard - is Excel hard?
%   \item Avoid manual analysis, provide selection of constraints
%   \item SOMEWHAT USED --Error checking
%   \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
% \end{itemize}

% \textbf{Novelty:}
% \begin{itemize}
%   \item USED -- Unsupervised setting (contrary to flashfill, etc)
%   \item Numeric, different constraints (contrary to single textual function solution in flashfill, etc)
%   \item USED -- Data format (2D) -- data is no longer in rows like a classic ML or DM settings
%   \item USED -- Declarative, general / modular, stacking of constraint problems
% \end{itemize}
%}

\begin{figure*}[tbh]
  \begin{center}
    \includegraphics[width=0.75\textwidth]{figures/Demo.png}
  \end{center}
  \vspace{-10pt}
  \caption{Example spreadsheet (black words and numbers only). Blue and green elements are added by us to clarify the relations.}
  \label{fig:main_example}
\end{figure*}

@@

\subsection{Error detection}
We consider two cases of error detection.
The first setting is the \textit{online} detection of errors which is similar to the autocompletion setting.
However, instead of considering viable constraints, we look at \textit{conflict} constraints, i.e. constraints that were learned at time~$t_0$ but do not agree with the newly added data.
Such conflict constraints can indicate an error in the input, however, they could also be accidental constraints that are invalidated by the new data.

The second type of error detection is \textit{offline} and attempts to detect errors in a spreadsheet.
Consider, for example, a use case concerning crime statistics provided by the FBI.
An extract of the spreadsheet is depicted in Figure~\ref{fig:fbi}.
When run on this sheet, our system is able to detect the second sum constraint, however, a missing value prevents the first sum constraint from being learned.

\sergey{We should explain Figure \ref{fig:fbi}, e.g. if we aggregate by the crime now, the missing value would not get into statistics, which seems faulty, since we can directly compute it.}

@@

@@

\section{Conclusions}

% points: 1) can be a base for an actual plugin or a function in excel 2) novel problem and challenge for systems and constraint solvers 3) can be part of the complicated pipeline togehter with the header detection
Our goal is to automatically identify constraints in a spreadsheet.
We have presented and evaluated our approach, implemented as the system \sname, that is able to learn a large set of constraints from CSV data.
Moreover, the amount of redundant constraints found by the system is limited despite the lack of more sophisticated post-processing steps.

\paragraph{Future work}
There are multiple directions for future work on this topic.
The system would be easier to use in an interactive setting where users can easily receive and provide feedback.
Moreover, the system can be adapted to produce less redundant constraints through the use of heuristic filtering.

Currently, the system only learns single constraints, however, extending it to nested constraints would allow more expressive concepts to be learned.
This shift would bring the approach in line with programming by example.

Aside from finding errors, the system can be extended to deal with noise and the ability to learn soft constraints.
Soft constraints are the (potentially weighted) constraints that hold only on some of the data.
This would extend the approach to new application domains as well as provide more native error detection.

\bibliographystyle{plain}
\bibliography{references}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\newcommand{\constraints}{\ensuremath{\mathcal{T}}\xspace}
\newcommand{\format}[1]{\textit{#1}\xspace}
\newcommand{\generategroups}{\format{generateGroups}}
\newcommand{\extractgroups}{\format{extractGroups}}
\newcommand{\extracttables}{\format{extractTables}}
\newcommand{\learnconstraints}{\format{learnConstraints}}
\newcommand{\findassignment}{\format{findConstraints}}
\newcommand{\postprocess}{\format{pruneRedundant}}
\newcommand{\constrainttorder}{\format{templateOrder}}
\newcommand{\template}{\format{constraint template}}

@@

{\it
\textbf{Motivation}:
\begin{itemize}
  \item USED -- File generated from model, model got lost, need to reconstruct
  \item Constraint programming is hard - is Excel hard?
  \item Avoid manual analysis, provide selection of constraints
  \item SOMEWHAT USED --Error checking
  \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
\end{itemize}

\textbf{Novelty:}
\begin{itemize}
  \item USED -- Unsupervised setting (contrary to flashfill, etc)
  \item Numeric, different constraints (contrary to single textual function solution in flashfill, etc)
  \item USED -- Data format (2D) -- data is no longer in rows like a classic ML or DM settings
  \item USED -- Declarative, general / modular, stacking of constraint problems
\end{itemize}

\begin{figure*}[tbh]
  \begin{center}
    \includegraphics[width=0.75\textwidth]{figures/Demo.png}
  \end{center}
  \vspace{-10pt}
  \caption{Example spreadsheet (black words and numbers only). Blue and green elements are added by us to clarify the relations.}
  \label{fig:main_example}
\end{figure*}
}

@@

@@

\subsection{Error detection}
We consider two cases of error detection.
The first setting is the \textit{online} detection of errors which is similar to the autocompletion setting.
However, instead of considering viable constraints, we look at \textit{conflict} constraints, i.e. constraints that were learned at time~$t_0$ but do not agree with the newly added data at time~$t_1$.
Such conflict constraints can indicate errors in the input.
Since conflict constraints could also be accidental constraints that are correctly invalidated by the new data, the size of the data at timet~$t_0$ should be large enough.

The second type of error detection is \textit{offline} and attempts to detect errors in a spreadsheet.
Consider, for example, a use case concerning crime statistics provided by the FBI.
An extract of the spreadsheet is depicted in Figure~\ref{fig:fbi}.
When run on this sheet, our system is able to detect the second sum constraint, however, a missing value prevents the first sum constraint from being learned.
A possible approach to detect such missing or wrong values is to look at a sample of the table that excludes the erroneous row and compare the constraints learned on this sample with the constraints learned by adding the row containing the mistake.
The sample needs to large enough such that we have enough confidence that the constraints are correct.
If we define the sample to be our data at time~$t_0$ and the added row to be the additional input at~$t_1$, this task can be formulated as online error detection and dealt with in the same way.
Of course, generating large enough samples and rows (columns) to be added can be done in multiple ways.
In the limited case of detecting single errors one can leave out every row (column), consider the remaining data to be the sample and
and the left out row (column) to be new input.
\samuel{Should this be more specific?}

Error detection could be integrated more closely with the algorithm, reducing the computational complexity by looking for errors during the constraint learning phase.
This would, however, make the modeling constraints (considerably) more difficult.

@@

\section{Conclusions}
\sergey{link to the github with implementations and the dataset}

\sergey{Future version, extensions, declarative stuff, bla-bla here}

% points: 1) can be a base for an actual plugin or a function in excel 2) novel problem and challenge for systems and constraint solvers 3) can be part of the complicated pipeline togehter with the header detection
Our goal was to automatically identify constraints that hold in a spreadsheet.
We presented and evaluated an approach that is able to learn a large set of constraints from CSV data.
Moreover, the amount of redundant constraints found by the algorithm is limited despite the lack of more sophisticated post-processing steps.

\paragraph{Future work}
We see multiple directions for future work on this topic.
The system we presented would become more useful in an interactive setting where users can easily receive and provide feedback.
Moreover, the system could be adapted to deal with additional types and produce less redundant constraints through the use of (heuristic) filtering or post-processing.

Currently, the system only learns single constraints, however, extending this approach to nested constraints would allow more expressive concepts to be learned.
This shift would bring the approach closer towards programming by example.

Aside from finding errors, the system could be extended to deal with noise and the ability to also learn soft constraints.
Soft constraints are (potentially weighted) constraints that hold only on some of the data.
This could extend the approach to new application domains as well as provide more native error detection.

\bibliographystyle{ecai}
\bibliography{references}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
